---
title: "Cascade Report for `r input$selectCountry`"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

Welcome to the cascade report. This report was generated on `r Sys.time()` from your own simulations. Caution this report is written dynamically, so please report any bugs or issues to [jack.olney11@imperial.ac.uk](mailto:jack.olney11@imperial.ac.uk).

The intention of this report is to act as a reference for any data entered, simulations carried out and results generated. The model is still under active development so caution is advised as results are preliminary.

# Setup

The country selected for cascade analysis was: `r input$selectCountry`

If any additional data was entered during setup it will be displayed below, else the table will appear blank:

Cascade Indicator                              | Value            | Source                  | Year
-----------------------------------------------|------------------|-------------------------|----------------------
Number of people living with HIV               | `r input$uPLHIV` | `r input$uPLHIV_source` | `r input$uPLHIV_year`
Number of people diagnosed with HIV            | `r input$uDIAG`  | `r input$uDIAG_source`  | `r input$uDIAG_year`
Number of people in HIV care                   | `r input$uCARE`  | `r input$uCARE_source`  | `r input$uCARE_year`
Number of people on ART                        | `r input$uART`   | `r input$uART_source`   | `r input$uART_year`
Number of people on ART and Virally Suppressed | `r input$uVIRAL` | `r input$uVIRAL_source` | `r input$uVIRAL_year`


## Data Review
Combining available data with any additional data entered by the user, the model used the following data on for calibration:

### Incidence Estimates
These incidence estimates were sourced from Spectrum. The model randomly sampled between the upper and lower bounds during calibration to account for uncertainty the in these incidence estimates.
```{r, fig.width = 7, fig.height = 3, fig.align = 'center', echo = FALSE}
    gridExtra::grid.table(scales::comma(MasterData$incidence))
```

### Cascade Data
The below table describes the entire cascade database used by the model for calibration. It is a tabular representation of what you would have seen on the calibration page. Calibration figures will be printed out ahead.
```{r, fig.width = 7, fig.height = 5, fig.align = 'center', echo = FALSE}
    gridExtra::grid.table(scales::comma(MasterData$calib))
```

### CD4 Distribution Estimates from Spectrum (2010)
To ensure that HIV-mortality rates were accurate, the model uses CD4 distribution estimates from 2010 (when calibration was started)
```{r, fig.width = 7, fig.height = 3, fig.align = 'center', echo = FALSE}
    int <- t(MasterData$cd4)
    proportion <- round(as.numeric(int[2:15,]), digits = 2)
    cd4 <- c(">500", "350-500", "250-350", "200-250", "100-200", "50-100", "<50")
    art <- c(rep("Off ART", 7), rep("On ART", 7))
    gridExtra::grid.table(data.frame(art, cd4, proportion))
```

# ### CD4 Distribution Estimates from Spectrum (2015)
# To ensure that the model retains the correct distribution of CD4 counts across both pre-ART and ART patients, we re-set the model to the 2015 CD4 distribution estimates.
# ```{r, fig.width = 7, fig.height = 3, fig.align = 'center', echo = FALSE}
#     int <- t(MasterCD4_2015)
#     proportion <- round(as.numeric(int[2:15,]), digits = 2)
#     cd4 <- c(">500", "350-500", "250-350", "200-250", "100-200", "50-100", "<50")
#     art <- c(rep("Off ART", 7), rep("On ART", 7))
#     gridExtra::grid.table(data.frame(art, cd4, proportion))
# ```

### Country Specific Treatment Guidelines
The impact of country-specific treatment guideline updates must be accounted by the model. We do not describe WHO Stage conditions so CD4 thresholds must be updated to reflect changing guidelines. Guidelines can be changed prior to calibration, and the values used during calibration are shown below.
```{r, fig.width = 7, fig.height = 3, fig.align = 'center', echo = FALSE}
    gridExtra::grid.table(MasterData$treatment_guidelines)
```
