---
title: "Cascade Report for `r input$selectCountry`"
author: Jack Olney
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: pdf_document
---

Welcome to the cascade report. This report was generated on `r Sys.time()` from your own simulations. Caution this report is written dynamically, so please report any bugs or issues to [jack.olney11@imperial.ac.uk](mailto:jack.olney11@imperial.ac.uk).

The intention of this report is to act as a reference for any data entered, simulations carried out and results generated. The model is still under active development so caution is advised as results are preliminary.

## Setup

The country selected for cascade analysis was: `r input$selectCountry`. Data entered during setup:

Cascade Indicator                              | Value            | Source                  | Year
-----------------------------------------------|------------------|-------------------------|----------------------
Number of people living with HIV               | `r input$uPLHIV` | `r input$uPLHIV_source` | `r input$uPLHIV_year`
Number of people diagnosed with HIV            | `r input$uDIAG`  | `r input$uDIAG_source`  | `r input$uDIAG_year`
Number of people in HIV care                   | `r input$uCARE`  | `r input$uCARE_source`  | `r input$uCARE_year`
Number of people on ART                        | `r input$uART`   | `r input$uART_source`   | `r input$uART_year`
Number of people on ART and Virally Suppressed | `r input$uVIRAL` | `r input$uVIRAL_source` | `r input$uVIRAL_year`

### Country Master Dataset

The values entered produced a final country dataset consisting of the following: _(format will be improved upon)_

```{r, echo = FALSE}
    MasterData
```

## Model Calibration

Given the values entered, calibration of the model produced the following figure:

```{r, echo = FALSE}
    BuildCalibrationPlots(data = CalibOut, originalData = MasterData, font = "Arial")
```

### Model Structure

The model has a following structure. Note, this is a simplified view of the structure, for more detail please view the official [model document](https://drive.google.com/file/d/0B02uVauBTUwhckJ1bG1QRmdwTGM/preview).

[model-flow-diagram]: www/ModelSimple.png "Model Diagram"

### Calibrated Parameters

Calibration produced many parameter sets, but for simplicity we will only show the upper and lower limits of parameters used:

Parameter | Upper                            | Lower
----------|----------------------------------|--------------------------------
$\rho$    | `r ParamMaxMin["rho"   , "max"]` | `r ParamMaxMin["rho"   , "min"]`
$q$       | `r ParamMaxMin["q"     , "max"]` | `r ParamMaxMin["q"     , "min"]`
$\gamma$  | `r ParamMaxMin["gamma" , "max"]` | `r ParamMaxMin["gamma" , "min"]`
$\theta$  | `r ParamMaxMin["theta" , "max"]` | `r ParamMaxMin["gamma" , "min"]`
$\kappa$  | `r ParamMaxMin["kappa" , "max"]` | `r ParamMaxMin["gamma" , "min"]`
$\omega$  | `r ParamMaxMin["omega" , "max"]` | `r ParamMaxMin["gamma" , "min"]`
$\mu$     | `r ParamMaxMin["mu"    , "max"]` | `r ParamMaxMin["gamma" , "min"]`
$p$       | `r ParamMaxMin["p"     , "max"]` | `r ParamMaxMin["gamma" , "min"]`

## Cascade Results

### Cascade Projection

```{r, echo = FALSE}
    GenCascadePlot(font = "Arial")
```

### Cascade Projection (discrete)

```{r, echo = FALSE}
    GenPowersCascadePlot(font = "Arial")
```

### UNAIDS 90-90-90

```{r, echo = FALSE}
    Gen909090Plot(font = "Arial")
```

### HIV Incidence

```{r, echo = FALSE}
    GenNewInfPlot(wizard = FALSE)
```

### AIDS-related Deaths

```{r, echo = FALSE}
    GenAidsDeathsPlot(wizard = FALSE)
```

Check this out for more information. http://rmarkdown.rstudio.com/authoring_basics.html
